Curiosity-Driven Development of Tool Use Precursors: a Robotic Model

### 2016-01-29 cogsci2016/paper.tex
intro

	The ontegenetic development of tool use shows different properties \cite{guerin2013survey}: 
	representations are grounded on a large amount of experiences and follow an ongoing process of upgrading [cite others?].
	In this paper we focus on one important property in the development of precursors of tool use which is the seamless progression 
	between overlapping phases of behavior with tools and objects which have been called overlapping waves \cite{siegler1996emerging}. 
	The behavioral study of these phases differentiate three categories of behaviors \cite{guerin2013survey}.
	In the first phase, from birth to one year old, babies engage in behaviors without objects, in the second phase, from 4-5 months old, their behavior shifts towards more interaction with a single object, and from 9 months old, begins a simple relational play with several objects.
	[more details?]

@@

@@

	\subsection{F-AGB vs H-RGB-P-AMB vs H-RGB-GR-AMB}

@@

>>>>

	The ontegenetic development of tool use shows different properties \cite{guerin2013survey}: 
	representations are grounded on a large amount of experiences and follow an ongoing process of upgrading [cite others?].
	In this paper we focus on one important property in the development of precursors of tool use which is the seamless progression 
	between overlapping phases of behavior with tools and objects, which have been called overlapping waves \cite{siegler1996emerging}. 
	The behavioral study of these phases differentiate three categories of behaviors \cite{guerin2013survey}.
	In the first phase, from birth to one year old, babies engage in behaviors without objects, in the second phase, from 4-5 months old, their behavior shifts towards more interaction with a single object, and from 9 months old, begins a simple relational play with several objects.
	[more details?]

@@

	To our knowledge, this model is the first to show overlapping waves structure in the development of tool use [can we say it is the first model of curiosity-driven development of tool use ?].

@@

	\subsection{F-RGB vs H-RGB-P-AMB vs H-RGB-GR-AMB}

		Results show different structures of behavior evolution in those 3 conditions.

@@

		Different structure of tool choice: overlapping waves of strategies to fulfill given goals in condition H-RGB-P-AMB-PGITC.
